formula1

### 2020-06-12 inst/f1points.Rmd
more work

From the above, we see that the first two drivers (Hamilton, Vettel)
are are respectively first and second according to both ranking
ranking procedures; but RAikkOnen 
*crap problem: latex ignores  diaeresis directive* and Bottas are third and fourth, and fourth and
third, according to points and likelihood respectively.  The degree of
agreement between the two systems might be quantified as "two", for
the positions of the top two drivers agree.

We can now assess objectively a given points system: using random
sampling techniques we can repeatedly generate an order table \emph{in
silico}, using estimated driver strengths from the 2017 table.  Given
a synthetic table, calculate drivers' maximum likelihood
\citeauthor{plackett1975} strengths, and also their points awarded
according to any given points system.  We then compare rankings
generated by the \citeauthor{plackett1975} strengths and the points
awarded and note the degree of agreement between the two.  This
furnishes an objective assessment of the points system used.

@@

	goodnesses <- seq_along(pointslist)
	for(i in seq_along(pointslist)){
		p_star <- ordertable2points(as.ordertable(ranktable_to_ordertable(random_table)),pointslist[[i]])
		p_star <- sort(p_star,decreasing=TRUE)
		p_star[] <- seq_along(p_star)
		goodness <- sum(cumprod(names(p_star)==names(l_star)))
		goodnesses[i] <- goodness
		}
	return(goodnesses)
}
pointslist <- list(
	real = points_real,
	line = top:1,
	top1 = rep(1,1),
	top2 = rep(1,2),
	top3 = rep(1,3),
	top4 = rep(1,4),
	zipf = 1/seq_len(top),
	exp2 = 1/2^seq_along(top),	
	exp3 = 1/3^seq_along(top),	
	exp4 = 1/4^seq_along(top)
)
```

```{r,label=multiplemontecarloexecute, cache=TRUE,echo=FALSE}
f2017 <- read.table("formula1_2017.txt",header=TRUE)[seq_len(top),1:20]
m <- maxp(ordertable2supp(as.ordertable(f2017)))
OO <- replicate(500+500,resampling_multiple(m,f2017,pointslist=pointslist))
```

@@

>>>>

From the above, we see that the first two drivers (Hamilton, Vettel)
are are respectively first and second according to both ranking
ranking procedures; but R\"{a}ikk\"{o}nen *yes I know it is wrong:
rmarkdown is defective* and Bottas are third and fourth, and fourth
and third, according to points and likelihood respectively.  The
degree of agreement between the two systems might be quantified as
"two", for the positions of the top two drivers agree.

Observing that both the likelihood ranking and the points ranking are
random variables suggests a method whereby we can objectively assess a
given points system.  Using sampling techniques we can repeatedly
generate an order table \emph{in silico}, using estimated driver
strengths from the observed 2017 table.  For each of, say, 1000 such
synthetic tables, calculate drivers' maximum likelihood
\citeauthor{plackett1975} strengths, and also their points awarded
according to any given points system.  We then compare rankings
generated by the \citeauthor{plackett1975} strengths and the points
awarded and note the degree of agreement between the two.  This
furnishes an objective assessment of the points system used.

@@

	goodnesses <- seq_along(pointslist)
	for(i in seq_along(pointslist)){
		p_star <- ordertable2points(as.ordertable(ranktable_to_ordertable(random_table)),pointslist[[i]])
		p_star <- sort(p_star,decreasing=TRUE)
		p_star[] <- seq_along(p_star)
		goodness <- sum(cumprod(names(p_star)==names(l_star)))
		goodnesses[i] <- goodness
		}
	return(goodnesses)
}
pointslist <- list(
	real = points_real,
	top1 = rep(1,1),
	top2 = rep(1,2),
	top3 = rep(1,3),
	top4 = rep(1,4),
	top5 = rep(1,5),
	top6 = rep(1,6),
	top7 = rep(1,7),
	top8 = rep(1,8),
	top9 = rep(1,9),
	topt = rep(1,10),  # effectively punishing the last finisher
   	lin1 = 1,   # same as top1
	lin2 = 2:1,
	lin3 = 3:1,
	lin4 = 4:1,
	lin5 = 5:1,
	lin6 = 6:1,
	lin7 = 7:1,
	lin8 = 8:1,
	lin9 = 9:1,
	lint = 10:1,
	line = 11:1,
	zipf = 1/seq_len(top),
	expa = 1/1.01^seq_len(top),
	expb = 1/1.10^seq_len(top),
	expc = 1/1.20^seq_len(top),
	expd = 1/1.50^seq_len(top),
	exp2 = 1/2^seq_len(top),
	exp3 = 1/3^seq_len(top),
	exp4 = 1/4^seq_len(top)
)
```

```{r,label=multiplemontecarloexecute, cache=TRUE,echo=FALSE}
f2017 <- read.table("formula1_2017.txt",header=TRUE)[seq_len(top),1:20]
m <- maxp(ordertable2supp(as.ordertable(f2017)))
OO <- replicate(1000,resampling_multiple(m,f2017,pointslist=pointslist))
```

@@

`r sin(1)`
